Programmer friendly communication framework

### 2024-03-02 2024_paper/paper/msglink_framework.tex
restructured and added info

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{caption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The role of passwords in cybersecurity and robotics}
\author{\IEEEauthorblockN{1\textsuperscript{st} Lilo Zobl}
\IEEEauthorblockA{\textit{Botball Team HTL Anichstraße} \\
\textit{HTL Anichstraße}\\
Innsbruck, Austria \\
lzobl@tsn.at}
\and
\IEEEauthorblockN{2\textsuperscript{th} Lukas Krahbichler}
\IEEEauthorblockA{\textit{Botball Team HTL Anichstraße} \\
\textit{HTL Anichstraße}\\
Innsbruck, Austria \\
lkrahbichler@tsn.at}
\and
\IEEEauthorblockN{3\textsuperscript{nd} Matteo Reiter}
\IEEEauthorblockA{\textit{Botball Team HTL Anichstraße} \\
\textit{HTL Anichstraße}\\
Innsbruck, Austria \\
mareiter@tsn.at}
\and
\IEEEauthorblockN{4\textsuperscript{rd} Niclas Prantl}
\IEEEauthorblockA{\textit{Botball Team HTL Anichstraße} \\
\textit{HTL Anichstraße}\\
Innsbruck, Austria \\
nprantl@tsn.at }
}
\maketitle

\begin{abstract}
This document will focus on an important topic of cybersecurity: Passwords. It will have a look on the indispensable role of passwords now and in the future. Additionally it will cover the role of passwords in robotics and will provide a best practice guide for working with password safes and how to create a secure and easy to remember master passphrase.

\end{abstract}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{caption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Programmer friendly communication framework}

\author{
    \IEEEauthorblockN{1\textsuperscript{st} Lilo Zobl}
    \IEEEauthorblockA{
        \textit{Botball Team FrenchBakery} \\
        \textit{HTL Anichstraße}\\
        Innsbruck, Austria \\
        lzobl@tsn.at
    }
    \and
    \IEEEauthorblockN{2\textsuperscript{nd} Matteo Reiter}
    \IEEEauthorblockA{
        \textit{Botball Team FrenchBakery} \\
        \textit{HTL Anichstraße}\\
        Innsbruck, Austria \\
        mareiter@tsn.at
    }
}

\maketitle

\begin{abstract}
This document will focus on an important topic of cybersecurity: Passwords. It will have a look on the indispensable role of passwords now and in the future. Additionally it will cover the role of passwords in robotics and will provide a best practice guide for working with password safes and how to create a secure and easy to remember master passphrase.
\end{abstract}
